DynaProg for Scala

### 2013-01-16 docs/report/report.tex
Nits.

\documentclass[11pt]{article}
\input{inc/style.sty}
\usepackage{multicol}
\usepackage{etoolbox}

@@

\section{Usage} \label{usage}
{\color{red} usage, make reference from problems to usage

@@

\begin{verbatim}
NEW:
- CPU: Dynaprog vs ADPFusion vs RNAfold vs GAPC
- GPU: (Zuker) Dynaprog vs GAPC (si on arrive a faire marcher)
- GPU: (MatMult) Dynaprog vs ATLP
- GPU: (SWat) Dynaprog vs  CUDAlign
\begin{verbatim}

@@

\subsubsection{Test 1 : Ad-hoc VS CUDA parsers (implies ATLP rescaled comparison)}

\subsubsection{Test 2 : CUDAlign vs CUDA parsers for small sequences}
Also CUDASW++

\subsubsection{Test 3 : GAPC vs Java parsers vs CUDA parsers}

\subsubsection{Test 4 ? : GPU RNAfolding vs CUDA parsers}

\subsection{Java parsers}
{\color{red}
MatrixMult-512, Mac+JDK7\ul
\item Original: 24.937 sec / 24.658 sec
\item Optimized concatenation: 19.329 sec / 18.924 sec
\item Tabulation as arrays+inline: 14.976 sec / 14.849 sec
\ule}

@@

>>>>

\documentclass[11pt]{article}
\input{inc/style.sty}
\usepackage{multicol,nameref}
\usepackage{etoolbox}

@@

\section{Usage} \label{usage}

Example based
- Matrix mult + parenthesizing
- SWat / Needleman

go check the examples/ folder

List of options at the end

{\color{red} usage, make reference from problems to usage

@@

\subsubsection{Test Scala / C / CUDA}
\subsubsection{Test 1 : CPU MatrixMult VS hand optimized VS GAPC VS ADPFusion)}
\subsubsection{Test 2 : GPU MatirxMult VS hand optimized VS ATLP)}
\subsubsection{Test 3 : CPU SWat VS hand optimized VS GAPC VS ADPFusion)}
\subsubsection{Test 4 : GPU SWat VS hand optimized VS CUDAlign)}
\subsubsection{Test 5 : CPU Zuker VS GAPC VS ADPFusion VS ViennaRNA)}
\subsubsection{Test 6 : GPU Zuker VS RNAFold?/Lavenier VS ViennaRNA-OpenCL)}

@@

\subsection{Scala parsers}
{\color{red}
MatrixMult-512, Mac+JDK7\ul
\item Original: 24.937 sec / 24.658 sec
\item Optimized concatenation: 19.329 sec / 18.924 sec
\item Tabulation as arrays+inline: 14.976 sec / 14.849 sec
\ule}

@@

\begin{verbatim}

recap of the report

recap of the results

big picture: with actual compiler technology we 
Embedded DSL vs external DSL
Larger picture how to go further

\end{verbatim}
